---
title: "Project Part 3" 
author: "Jeffrey Shi"
fontsize: 12pt
geometry: margin=1in
urlcolor: black
output: pdf_document
header-includes:
- \usepackage{setspace}
- \onehalfspacing
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, highlight=FALSE)
library(BSDA)
library(UsingR)
library(OpenMx)
library(ggplot2)
library(pwr)
```

```{r, echo=FALSE}
fifa<-read.csv("data.csv")
europe<-read.csv("europe.csv")
europe<-europe$Country
samerica<-c("Argentina", "Bolivia", "Brazil", "Chile", "Colombia", "Ecuador", "Guyana", "Paraguay", "Peru", "Suriname", "Uruguay", "Venezuela")
```

## Question  
My data set contains complete FIFA 19 player data, which has many columns that are 'grouped' together. The first few columns are general player data, including their unique ID and age. Next they have some basic player data such as their strength in the game and their wages, etc. Then there is more detailed and specific player data such as their strenth of their right foot, etc. One of the main differentiators of the data is the nationality of each player. One question to be tested is: Using the 'Overall' stat of the players, is there evidence that players from European countries are better (meaning higher Overall stat) than players from South American countries? I chose to test players from these two continents because these two continents are known for to yield the best players in the world and are known to be overall heavily invested in soccer. This data is applicable for this question because the dataset is a complete population for professional soccer players and subsetting if for European and South American players also yields complete populations so sampling from this set of data will yield accurate results.


##Data isolation
First, I isolate the parts of the data that I will be using, the first being the set of all European players and the second being the set of all South American players and I also ensured that any player with NA as their Overall is omitted. There are just over 3000 South American players and almost 8000 European players so the populations are quite large.
```{r}
europe1<-na.omit(fifa[which(fifa$Nationality%in% europe),])
samerica1<-na.omit(fifa[which(fifa$Nationality%in%samerica),])
```

##Test selection
For testing the question stated above, I have chosen to use the 2-sample z-test since the population standard deviation is known for European and South-American players. In addition, each sample is independent. In addition, for this sampling, I will take samples of 1000 since the population is so large and with the larger sample size, the Central Limit Theorem will apply and the power of the test increases so the probability of a type II error also decreases. This means that the result of the test can be easily generalized to the whole population due to the low type II error and the large sample size.

##Data selection
As mentioned above, I'm taking samples of 1000 players from both populations so I take a sampling of 1000 random numbers within the size of the populations I'm drawing from and then taking those rows from the population as the sample.
```{r}
samp1<-sample(1:7941, 1000)
samp2<-sample(1:3176, 1000)
EuropeanPlayers<-europe1[samp1,]$Overall
SouthAmericanPlayers<-samerica1[samp2,]$Overall
```
##Testing
```{r}
europeRating<-europe1$Overall
samericaRating<-samerica1$Overall
sig1<-var(europeRating)
sig2<-var(samericaRating)

z.test(EuropeanPlayers, SouthAmericanPlayers, mu=0, 
       sigma.x=sig1, sigma.y=sig2, alternative="greater")
```

##Conclusion
From the test done above, we see that the p-value is quite high, 0.6739, so we accept the null hypothesis that there is no significant difference in the population means. With the data given, this means that there isn't sufficient evidence that the mean skill level of professional European players is any different than the mean skill level of professional South American players. Looking at the means, there is a slight difference, but considering the popualtion sizes, that difference is not significant enough to be generalized to the entire population of players for certain.

## References
1. <https://www.kaggle.com/karangadiya/fifa19>
2. <http://www.3rs-reduction.co.uk/html/6__power_and_sample_size.html>
